---
title: "Quadvariate Viz"
---

Use this file to generate a professional looking **quadvariate** visualization.  The visualization will not perfect the first time but you are expected to improve on it throughout the semester especially after covering advanced topics such as effective viz.

```{r}
library(tidyverse)
library(mosaic)
library(fivethirtyeight)
library(ggplot2)
```
Data on number of births a month, year, day and what day, month year.
```{r}
data("Birthdays")
daily_births <- Birthdays %>% 
  group_by(date) %>%
  summarize(births = sum(births)) %>%
  mutate(year = year(date), 
         month = month(date, label = TRUE),
         day_of_month = mday(date),
         day_of_week = wday(date, label = TRUE))
```

This visualization uses faceted colored box-plots to illustrate the number of births per year and how those differed in each month on each day of the week. 
```{r}
ggplot(daily_births, aes(x=year, y=births, fill=month)) +
  geom_boxplot() +
  facet_wrap(~day_of_week)
```
