---
title: "Multiviz"
format: html
---
```{r}
library(tidyverse)

# Import data
weather <- read.csv("https://mac-stat.github.io/data/weather_3_locations.csv") |> 
  mutate(date = as.Date(date))  

# Check out the first 6 rows
head(weather)
# What are the units of observation?
#places

# How many data points do we have? 
#2367

# What type of variables do we have?
str(weather)
#num, chr, int
```
```{r}
# Plot 1 (no facets & starting from a density plot of temp3pm)
ggplot(weather, aes(x = temp3pm, fill = location)) + 
  geom_density(alpha = 0.5)
```







```{r}
# Plot temp3pm vs temp9am
# Change the code in order to indicate the location to which each data point corresponds
ggplot(weather, aes(y = temp3pm, x = temp9am)) + 
  geom_point()
```


```{r}
# Don't worry about the syntax (we'll learn it soon)
woll <- weather |>
  filter(location == "Wollongong") |> 
  mutate(date = as.Date(date))  
```

```{r}
# How often does it raintoday?
# Fill your geometric layer with the color blue.
ggplot(woll, aes(x = raintoday, fill = raintomorrow)) +
  geom_bar(position = "dodge")
```

```{r}
# Instead of a curve that captures the general TREND,
# draw a line that illustrates the movement of RAW temperatures from day to day
# NOTE: We haven't learned this geom yet! Guess.
ggplot(woll, aes(y = temp3pm, x = date)) +
  geom_line()
```

```{r}
# Plot temp3pm vs temp9am
# Change the code in order to indicate the location to which each data point corresponds
ggplot(weather, aes(y = temp3pm, x = temp9am, color = location)) + 
  geom_point() +
  scale_fill_manual(values = c("blue","red","yellow"))
```

```{r}
# Change the code in order to indicate the location to which each data point corresponds
# AND identify the days on which it rained / didn't raintoday
ggplot(weather, aes(y = temp3pm, x = temp9am, color = location)) + 
  geom_point() +
  scale_fill_manual(values = c("blue","red","yellow")) +
  facet_wrap(~raintoday)
```

```{r}
# Change the code in order to construct a line plot of temp3pm vs date for each separate location (no points!)
ggplot(weather, aes(y = temp3pm, x = date, color = location)) + 
  geom_line()
```

```{r}
# Plot the relationship of raintomorrow & raintoday
# Change the code in order to indicate this relationship by location
ggplot(weather, aes(x = raintoday, fill = raintomorrow)) + 
  geom_bar(position = "fill") + 
  facet_wrap(~ location)
```

```{r}
# Import and check out data
education <- read.csv("https://mac-stat.github.io/data/sat.csv")
head(education)
```
```{r}
ggplot(education, aes(x=sat)) +
  geom_histogram(color = "white") 
#Summarize your observations from the plot. Comment on the basics: range, typical outcomes, shape. (Any theories about what might explain this non-normal shape?)
# Scores range from around 800 to 1100, peak at 900, fewer scores between about 950 and 1000
```

```{r}
# Construct a plot of sat vs expend
# Include a "best fit linear regression model" (HINT: method = "lm")
ggplot(education, aes(x=expend, y=sat)) +
  geom_point() +
  geom_smooth(method = lm)
```

```{r}
# Construct a plot of sat vs salary
# Include a "best fit linear regression model" (HINT: method = "lm")
ggplot(education, aes(x=salary, y=sat)) +
  geom_point() +
  geom_smooth(method=lm)
```
What are the relationship trends between SAT scores and spending? Is there anything that surprises you?

- There seems to be a negative relationship between SAT scores and spending which is the opposite of what I would expect. Also a negative relationship between SAT scores and salary which is also opposite of what I would I expect.


```{r}
ggplot(education, aes(x=salary, y=sat, color = expend)) +
  geom_point() +
  geom_smooth(method=lm)
```

```{r}
ggplot(education, aes(y = sat, x = salary, color = cut(expend, 3))) + 
  geom_point() + 
  geom_smooth(se = FALSE, method = "lm")
```

Describe the trivariate relationship between sat, salary, and expend.

- As salary increases and as expenditure increases, SAT scores go down. There is a slight increase in SAT scores when salaries reach 45 and expenditure reaches 7.73

```{r}
ggplot(education, aes(x=fracCat)) +
  geom_bar(fill = "blue") +
  labs(y= "Number of States", x= "Fraction of Participants")
```

```{r}
ggplot(education, aes(x=fracCat, y=sat)) +
  geom_boxplot()
```

```{r}
ggplot(education, aes(x=fracCat, y=sat)) +
  geom_violin()
```

```{r}
ggplot(education, aes(x=expend, y=sat, color = fracCat)) +
  geom_point() +
  geom_smooth(method = lm)
```
It seems SAT scores do not decrease as expenditure increases and it increases slightly for states where a low and states where a high percentage of students take the test, and the relationship is even more positive when the percentage of students who take the test is medium. It may have looked like it decreased because percentage of people taking the test was not taken into account.






